Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-24 paper.tex
Update Paper
Experiment section completed. Beginning with the Discussion.
Updated Paper
Work in progress.

            The third experiment objective was to confirm Animal Life Cycle
            Algorithm continued finding solutions in a reduced number of
            evaluations. For this test, we selected the Griewank Benchmark
            Function for Optimization. Figure~\ref{fig.fun_griewank} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_griewank5} and~\ref{tab.fun_griewank10} 
            (for five and ten dimensions, respectively). With this analysis, 
            we confirmed our strategy continued to obtain solutions in the same 
            order as expected, in a reduced number of evaluations, in less time.

@@

    \subsection{ALTO / HASTA AQUI VAMOS}

@@

>>>>

            The third experiment objective was to confirm Animal Life Cycle
            Algorithm continued finding solutions in a reduced number of
            evaluations. For this test, we selected the Griewank Benchmark
            Function for Optimization. Figure~\ref{fig.fun_griewank} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_griewank5} and~\ref{tab.fun_griewank10} 
            (for five and ten dimensions, respectively). With this analysis, 
            we confirmed our strategy continued to obtain solutions in the same 
            order as expected, in a reduced number of evaluations and less time.

@@

@@

***********************
ALTO / HASTA AQUI VAMOS
***********************
